Using Deep Learning to Identify Patients with Cognitive Impairment in Electronic Health Records

### 2021-09-12 Submission/Paper/ML4H/Paper.tex
authors added

\author{Tanish Tyagi \nametag{\thanks{Authors contributed equally}\SUP{1}},
Colin G. Magdamo\nametag{\footnotemark[1]\SUP{1}}, 
Ayush Noori \SUP{1},
Mayuresh Deodhar \SUP{1},
Zhuoqiao Hong \SUP{1},
Alberto Serrano-Pozo \SUP{1},
Dimitry Propenko \SUP{1},
Rudy E. Tanzi \SUP{1},
Deborah Blacker \SUP{1},
Bradley T. Hyman \SUP{1},
Shibani S. Mukerji \SUP{1},
M. Brandon Westover \SUP{1},
Sudeshna Das\SUP{1},
\centering \Email{
\\[\bigskipamount] 
\SUP{1}\{ttyagi, 
cmagdamo,
anoori1,
...
sdas5\}
@mgh.harvard.edu}
% 
\begin{center}\addr Massachusetts General Hospital, Boston, MA\end{center}
}

>>>>

\author{Tanish Tyagi \nametag{\thanks{Authors contributed equally}\SUP{1}},
Colin G. Magdamo\nametag{\footnotemark[1]\SUP{1}}, 
Ayush Noori \SUP{1},
Mayuresh Deodhar \SUP{1},
Zhuoqiao Hong \SUP{1},
Alberto Serrano-Pozo \SUP{1},
Dimitry Prokopenko \SUP{1},
Rudy E. Tanzi \SUP{2},
Deborah Blacker \SUP{1},
Bradley T. Hyman \SUP{1},
Shibani S. Mukerji \SUP{1},
M. Brandon Westover \SUP{1},
Sudeshna Das\SUP{1},
\centering \Email{
\\[\bigskipamount] 
\SUP{1}\{ttyagi, 
cmagdamo,
anoori1,
mdeodhar,
zhong1,
aserrano1,
dprokopenko,
dblacker,
bhyman,
smukerji,
mwestover,
sdas5\}
@mgh.harvard.edu}
\centering \Email{
\\[\bigskipamount] 
\SUP{2}\{tanzi
\}@helix.mgh.harvard.edu
}
% 
\begin{center}\addr Massachusetts General Hospital, Boston, MA\end{center}
}
